Positivity-Preserving Adaptive Runge--Kutta Methods

### 2020-05-05 nusslein_vsrp/latex/overview.tex
Changed Pseudocode cf. #22
additional minor revision

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\State Initialize $n \leftarrow 0$, $u^n \leftarrow u_0$, $t \leftarrow 0$
\While{$t<t_{end}$}
\State Choose $\Delta t$ (fixed or via an adaptive stepsize control)
\State Calculate $F = (f_1, \dots, f_s)$, cf.\ \eqref{eq:stagevalues}
\State $u^{n+1} \leftarrow u^n + \Delta t Fb$, cf.\ \eqref{eq:Combination}
\If {$u^{n+1} \geq 0$}
	\State $success \leftarrow True$
\Else
	\State{$\pt \leftarrow p_{start}$}
	\While{$\pt \geq p_{min}$}
		\State Solve LP \eqref{eq:free-adaptation}
		\If {LP is feasible \textbf{and} result is correct} \todo{TODO: define these}
			\State $\delta \leftarrow \| \Delta t F(\bt-b)\|$
			\If {$\delta < tol$}
				\State $u^{n+1} \leftarrow u^n+\Delta t F \tilde b$
				\State $success \leftarrow True$
				\State \textbf{break}
			\EndIf
		\EndIf
		\If {$\pt = p_{min}$}
			\State $sucess \leftarrow False$
		\EndIf
		\State $\pt \leftarrow \pt - 1$
	\EndWhile
\EndIf
\If {$sucess$}
	\State $t \leftarrow t + \dt$, $n \leftarrow n+1$ and continue
\Else
  \State \todo{TODO}
\EndIf
\EndWhile
\end{algorithmic}
\caption{Pseudocode for the algorithm using a free adaption of weights.}
\label{alg:Adaption}
\end{algorithm}

@@

    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{plots/ADP_sol_27.pdf}
        \caption{$t=27$.}
        \label{fig:sol_ADP27}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{plots/ADP_sol_50.pdf}
        \caption{$t=50$.}
        \label{fig:sol_ADP50}
    \end{subfigure}
    \caption{Solution of advection-diffusion-reaction problem \eqref{eq:ADR} at different times.}\label{fig:Sol_ADP}
\end{figure}

>>>>

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\State Initialize $n \leftarrow 0$, $u^n \leftarrow u_0$, $t \leftarrow 0$
\While{$t<t_{end}$}
\State Choose $\Delta t$ (fixed or via an adaptive stepsize control)
\State Calculate $F = (f_1, \dots, f_s)$, cf.\ \eqref{eq:stagevalues} \label{line:calc_stge}
\State $u^{n+1} \leftarrow u^n + \Delta t Fb$, cf.\ \eqref{eq:Combination}
\If {$u^{n+1} \geq 0$}
	\State  \textbf{GOTO} line\,\ref{line:update}
\Else
	\State{$\pt \leftarrow p_{start}$}
	\While{$\pt \geq p_{min}$}
		\State Solve LP \eqref{eq:free-adaptation}
		\If {LP is feasible} 
			\State $\delta \leftarrow \| \Delta t F(\bt-b)\|$
			\If {$\delta < tol_\delta$}
				\State $u^{n+1} \leftarrow u^n+\Delta t F \tilde b$
				\State  \textbf{GOTO} line\,\ref{line:update} 
			\EndIf
		\EndIf
		\State $\pt \leftarrow \pt - 1$
	\EndWhile
	\State Reduce $\dt$
	\State \textbf{GOTO} line\,\ref{line:calc_stge} 
\EndIf
\State Calculate $error$ cf. \ref{eq:Err} \label{line:update} 
\If {$error \leq tol_{error}$}
	\State $t \leftarrow t + \dt$, $n \leftarrow n+1$ 
\Else
	\State Reduce $\dt$
	\State \textbf{GOTO} line\,\ref{line:calc_stge} 
\EndIf
\EndWhile
\end{algorithmic}
\caption{Pseudocode for the algorithm using a free adaption of weights.}
\label{alg:Adaption}
\end{algorithm}

@@

    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{plots/ADP_sol_27.pdf}
        \caption{$t=27$.}
        \label{fig:sol_ADP27}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{plots/ADP_sol_50.pdf}
        \caption{$t=50$.}
        \label{fig:sol_ADP50}
    \end{subfigure}
    \caption{Numerical solution of the advection-diffusion-reaction problem \eqref{eq:ADR} at different times.}\label{fig:Sol_ADP}
\end{figure}
